---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `read.cwa` package

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/muschellij2/read-cwa?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/read-cwa)
[![R build status](https://github.com/muschellij2/read.cwa/workflows/R-CMD-check/badge.svg)](https://github.com/muschellij2/read.cwa/actions)
<!-- badges: end -->

The goal of `read.cwa` is to provide functionality to convert 'Axivity' 'CWA' files (https://axivity.com/).  The data was extracted from https://github.com/digitalinteraction/openmovement/, specifically code from https://github.com/digitalinteraction/openmovement/tree/master/Software/AX3/cwa-convert/c, 
which has the following copyright:
> Copyright (c) 2009-2018, Newcastle University, UK.
All rights reserved.

## Installation

You can install the released version of `read.cwa` from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("read.cwa")
```

And the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("muschellij2/read.cwa")
```
## Example

This is a basic example which shows you how to read in a CWA file:

```{r example}
library(read.cwa)
file = system.file("extdata", "ax3_testfile.cwa.gz", package = "read.cwa")
out = read_cwa(file)
head(out)
```

```{r ex2}
out = read_cwa(file, xyz_only = TRUE)
head(out)
## basic example code
```

