---
title: "Reading-in-CWA-files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reading-in-CWA-files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here we will show a simple example of converting and reading in Continuous Wave Accelerometer (CWA) data files (https://axivity.com/userguides/ax3/using/).  First, let's load up the package.
```{r setup}
library(read.cwa)
```

# Converting to a CSV
We will use a file embedded in the package:
```{r}
file = system.file("extdata", "ax3_testfile.cwa.gz", package = "read.cwa")
```

To show how the package uses the C code from https://github.com/digitalinteraction/openmovement/tree/master/Software/AX3/cwa-convert/c to do the underlying CWA to CSV conversion.  The `convert_cwa` function will run to create a CSV file
```{r}
csv_file = convert_cwa(file, verbose = FALSE)
csv_file
```

We see the output is a list, with the first element being the `file` element, which is the CSV output file.  The `header` slot, if the `GGIR` package is available, will be header information from the file.  The C code does not output all the header elements, so `GGIR` was used.

If we look at the head of the CSV file, we see it has data only:
```{r}
readLines(csv_file$file, 3)
```

This CSV can be read in using `read_cwa_csv`:

```{r}
df = read_cwa_csv(csv_file$file)
head(df)
```
which will give you the output `data.frame`.

```{r}
attr(df, "header")
```

# Converting to a Data Frame
The process for converting a CWA to a `data.frame` is essentially the 2 processes above wrapped into the `read_cwa` function:

```{r}
out = read_cwa(file, verbose = FALSE)
out
```


If the header is not available, you can do a quick estimation of the sampling frequency based on the differences between times:

```{r}
diffs = as.numeric(diff(out$data$timestamp))
diffs = as.numeric(names(which.max(table(diffs))))
estimated_freq = round(1/diffs, 3)
estimated_freq
```

which should match up when you have the header information:

```{r}
out$header$frequency
```

## Reading in Other Data
By default, for all functions, the `xyz_only = TRUE`, which indicates only the time and X/Y/Z acceleration parameters will be reported.  If `xyz_only = FALSE`, then all data available from this extracted code will be retrieved from the data file:

```{r}
out = read_cwa(file, xyz_only = FALSE, verbose = FALSE)
out$data
```

where we see the following columns output:
```{r}
colnames(out$data)
```

